Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2018-05-22 RNARedPrint-Bioinfo2018.tex
minor change

We define the \emph{maximum separator size} $s$ as
$\max_{u,v\in V} | \separator{u}{v} |$ and denote the maximum size of
$\difference{u}{v}$ over $(u,v)\in\edgesToR{}$ as $D$.  In the absence
of specific optimizations, running Alg.~\ref{alg:pf} requires
$\mathcal{O}((|\F|+|V|)\cdot 4^{w+1})$ time and
$\mathcal{O}(|V|\cdot4^s)$ space
(Supp. Mat.~\ref{appsec:algcomplexity}); Alg.~\ref{alg:sampling} would
require $\mathcal{O}((|\F|+|V|)\cdot 4^D)$ per sample on arbitrary
tree decompositions
(Supp. Mat.~\ref{appsec:algcomplexity}). W.l.o.g. we assume that
$D=1$; note that tree decompositions can generally be transformed,
such that $\difference{u}{v}\leq 1$.
%
Moreover, the size of $\F$ is linearly bounded: for $k$
input structures for sequences of length $n$, the energy function is
expressed by $\mathcal{O}(n\,k)$ functions. Finally, the number of cluster
tree nodes is in $O(n)$, such that $|\F|+|V| \in \mathcal{O}(n\,k)$.

>>>>

We define the \emph{maximum separator size} $s$ as
$\max_{u,v\in V} | \separator{u}{v} |$ and denote by  $D$ the maximum size of
$\difference{u}{v}$ over $(u,v)\in\edgesToR{}$.  In the absence
of specific optimizations, running Alg.~\ref{alg:pf} requires
$\mathcal{O}((|\F|+|V|)\cdot 4^{w+1})$ time and
$\mathcal{O}(|V|\cdot4^s)$ space
(Supp. Mat.~\ref{appsec:algcomplexity}); Alg.~\ref{alg:sampling} would
require $\mathcal{O}((|\F|+|V|)\cdot 4^D)$ per sample on arbitrary
tree decompositions
(Supp. Mat.~\ref{appsec:algcomplexity}). W.l.o.g. we assume that
$D=1$; note that tree decompositions can generally be transformed,
such that $\difference{u}{v}\leq 1$.
%
Moreover, the size of $\F$ is linearly bounded: for $k$
input structures for sequences of length $n$, the energy function is
expressed by $\mathcal{O}(n\,k)$ functions. Finally, the number of cluster
tree nodes is in $O(n)$, such that $|\F|+|V| \in \mathcal{O}(n\,k)$.
